Transmembrane helices are an over-presented and evolutionarily conserved source of major histocompatibility complex class I and II epitopes

### 2021-12-29 bbbq_article.tex
Fix wording, thanks Geert

To determine the evolutionary conservation of TMHs,
we first collected human single nucleotide polymorphisms (SNPs) 
resulting in a single amino acid substitution to determine if this occurred within a predicted TMH or not.

>>>>

To determine the evolutionary conservation of TMHs, we first
collected human single nucleotide polymorphisms (SNPs)
resulting in a single amino acid substitution and determined if
this occurred within a predicted TMH or not.
